Concurrent and Distributed Programming in Harmony

### 2022-01-13 paper/paper.tex
Improved code a bit

def thread(self):
    let op = choose({ "deq", "enq" }):
        if op == "enq":
            print("call enqueue", self)
            queue.enqueue(?q, self)
            print("done enqueue", self)
        else:
            print("call dequeue", self)
            let v = queue.dequeue(?q):
                print("done dequeue", self, v)

>>>>

def thread(self):
    if choose({ "deq", "enq" }) == "enq":
        print("call enqueue", self)
        queue.enqueue(?q, self)
        print("done enqueue", self)
    else:
        print("call dequeue", self)
        let v = queue.dequeue(?q):
            print("done dequeue", self, v)
